Squintability and Other Metrics for Assessing Projection Pursuit Indexes, and Guiding Optimisation Choices

### 2025-03-02 jso.tex
merged changes with Sherry

\begin{tcolorbox}[enhanced jigsaw, colback=white, opacitybacktitle=0.6, arc=.35mm, colbacktitle=quarto-callout-note-color!10!white, toptitle=1mm, opacityback=0, breakable, bottomrule=.15mm, bottomtitle=1mm, titlerule=0mm, coltitle=black, colframe=quarto-callout-note-color-frame, title={Algorithm: Jellyfish Optimizer Pseudo Code}, rightrule=.15mm, toprule=.15mm, leftrule=.75mm, left=2mm]

>>>>

\begin{tcolorbox}[enhanced jigsaw, colback=white, colbacktitle=quarto-callout-note-color!10!white, opacitybacktitle=0.6, opacityback=0, bottomtitle=1mm, leftrule=.75mm, breakable, arc=.35mm, colframe=quarto-callout-note-color-frame, title={Algorithm: Jellyfish Optimizer Pseudo Code}, coltitle=black, titlerule=0mm, toptitle=1mm, rightrule=.15mm, left=2mm, toprule=.15mm, bottomrule=.15mm]
